---
title: "simpleRegress"
author: "Jake Glickman"
date: "June 15, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

When comparing length to weight the adjusted R-squared was less than the adjusted R-squared when comparing length and neck size. Therefor using neck size to predict length was better than using weight.


```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```
When predicting length with head length the adjusted R- squared was larger than when predicting length with neck size. The residual standard error for head length is less than that of the neck size prediction. This tells us that predicting length using head length is a better comparison than using neck size to determine length.


```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

Using age to predict length was worse than using neck to predict length. This is due to the adjusted R-squared being smaller when predicting length with age and the residual standard error was larger.


```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

Using head width to predict length was worse than using neck to predict length. This is because the adjusted R-squared was smaller when predicting length with head width and the residual standard error was larger.

